A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-07-22 survey.tex
Table I, II and III: results with top bots.

\author{Santiago~Onta\~{n}\'{o}n\thanks{Santiago~Onta\~{n}\'{o}n is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Gabriel~Synnaeve\thanks{Gabriel~Synnaeve is with the Laboratory of Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm in Paris, France.},
        Alberto~Uriarte\thanks{Alberto Uriarte is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Florian~Richoux\thanks{Florian~Richoux is with the Laboratory of Computer Science of the University of Nantes, France.},
        David~Churchill\thanks{David~Churchill is with the Computing Science Department of the University of Alberta, Edmonton, Canada.},
        Mike~Preuss\thanks{Mike~Preuss is with the Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.}}

@@

\begin{table}[!t]
\caption{Results of the AIIDE 2010 competition}
\label{tab:aiide2010}
\centering
\begin{tabular}{|c|l|}
\hline
{\bfseries Position} & {\bfseries Bot}\\
\hline
1 & Overmind \\
2 & Krasi0 \\
3 & Chronos \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!b]
\caption{Results of the AIIDE 2011 competition}
\label{tab:aiide2011}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 88.9\% \\
2 & UAlbertaBot & 79.4\% \\
3 & AIUR & 70.3\% \\
4 & ItayUndermind & 65.8\% \\
5 & EISBot & 60.6\% \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Results of the AIIDE 2012 competition}
\label{tab:aiide2012}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 84.4\% \\
2 & AIUR & 72.2\% \\
3 & UAlbertaBot & 68.6\% \\
4 & BroodwarBotQ & 59.1\% \\
5 & AdjutantBot & 52.8\% \\
\hline
\end{tabular}
\end{table}

>>>>

\author{Santiago~Onta\~{n}\'{o}n\thanks{Santiago~Onta\~{n}\'{o}n is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Gabriel~Synnaeve\thanks{Gabriel~Synnaeve is with the Laboratory of Cognitive Science and Psycholinguistics (LSCP) of ENS Ulm in Paris, France.},
        Alberto~Uriarte\thanks{Alberto Uriarte is with the Computer Science Department at Drexel University, Philadelphia, PA, USA.},
        Florian~Richoux\thanks{Florian~Richoux is with the Nantes Atlantic Computer Science Laboratory, France.},
        David~Churchill\thanks{David~Churchill is with the Computing Science Department of the University of Alberta, Edmonton, Canada.},
        Mike~Preuss\thanks{Mike~Preuss is with the Department of Computer Science of Technische Universit{\"a}t Dortmund, Germany.}}

@@

\begin{table}[!t]
\caption{Ranking of the three best bots of the AIIDE 2010 competition}
\label{tab:aiide2010}
\centering
\begin{tabular}{|c|l|}
\hline
{\bfseries Position} & {\bfseries Bot}\\
\hline
1 & Overmind \\
2 & Krasi0 \\
3 & Chronos \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!b]
\caption{Results of the five best bots of the AIIDE 2011 competition}
\label{tab:aiide2011}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 88.9\% \\
2 & UAlbertaBot & 79.4\% \\
3 & AIUR & 70.3\% \\
4 & ItayUndermind & 65.8\% \\
5 & EISBot & 60.6\% \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Results of the five best bots of the AIIDE 2012 competition}
\label{tab:aiide2012}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 84.4\% \\
2 & AIUR & 72.2\% \\
3 & UAlbertaBot & 68.6\% \\
4 & BroodwarBotQ & 59.1\% \\
5 & AdjutantBot & 52.8\% \\
\hline
\end{tabular}
\end{table}
